---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `du`

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/du/workflows/R-CMD-check/badge.svg)](https://github.com/muschellij2/du/actions)
<!-- badges: end -->

The goal of `du` is to implement the data usage metric.

## Installation

You can install the released version of du from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("du")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("muschellij2/du")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(du)
```


```{r glm}
if (requireNamespace("MASS", quietly = TRUE)) {
  utils::data(anorexia, package = "MASS")

  anorex.1 <- glm(Postwt ~ Prewt + Treat + offset(Prewt),
                  family = gaussian, data = anorexia[ anorexia$Prewt > 70.25,])
  sub_df = anorexia[ anorexia$Postwt < 80 , c("Prewt", "Postwt"), drop = FALSE]
  sub_df2 = anorexia[ anorexia$Prewt > 70.25,]
  print(head(disk_usage(anorex.1, full_data = anorexia)))
  print(head(du(anorex.1, sub_df, sub_df2,
                full_data = anorexia)))
}
```

# Known Issues

The way things are found to be "used" is it is joined with the full data set.  If the new subsetted object (e.g. `data.frame`) is not unique, then the join will fail as it does some extra checking.
